Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae

### 2020-11-09 ccsn.tex
My last comments.

\begin{abstract}
The eventual detection of gravitational waves from core-collapse supernovae (CCSN) will help improve our current understanding of the explosion mechanism of massive stars. The stochastic nature of the late post-bounce gravitational wave signal due to matter effects and the large number of degrees of freedom of the phenomenon make the source parameter inference problem very challenging. In this paper we take a step towards that goal and present a parameter estimation approach which is based on the gravitational waves associated with convective oscillations of proto-neutron stars (PNS). Numerical simulations of CCNS have shown that buoyancy-driven g-modes are responsible for a significant fraction of the gravitational wave signal and their time-frequency evolution is linked to the physical properties of the compact remnant through universal relations, as demonstrated in~\cite{Torres:2019b}. We use a set of 1D CCSN simulations to build a model that relates the  evolution of the PNS properties with the frequency of the dominant g-mode, which is extracted from the gravitational-wave data using a new algorithm we have developed for our study. The model is used to infer the time evolution of combinations of the mass and the radius of the PNS. The performance of the method is estimated employing simulations of 2D CCSN waveforms covering a progenitor mass range between 11 and 40 solar masses and different equations of state. Considering signals embedded in Gaussian gravitational wave detector noise, we show that it is possible to infer PNS properties for a galactic source using Advanced LIGO and Advanced Virgo data at design sensitivities. Third generation detectors such as Einstein Telescope and Cosmic Explorer will allow to test distances of ${\cal O}(100\, {\rm kpc})$. %\tf{Caveats? Gaussian noise?}
% 
%  Core-collapse supernovae are very important phenomena in the Universe and their expected gravitational
%  waves emission is a promising tool to study the onset of the supernova explosion mechanism. The complexity
%  of the gravitational wave signal due to matter effects and the large degrees of freedom of the phenomena
%  makes the source parameter inference problem very challenging. In this paper, we have considered the
%  proto neutron star oscillation modes that carry out a large fraction of the gravitational wave signal and
%  whose frequency time evolution is linked to the system properties through universal relations as
%  demonstrated in ~\cite{Torres:2019b}. We have developed a simple algorithm to extract from the
%  gravitational wave data the frequency evolution of the gravity mode. A set of 1D core collapse
%  supernova simulations is used to build a model of evolution of the proto neutron star properties
%  with the gravity mode frequency. The model is then used to infer the time evolution of a combinaison of
%  the radius and mass of the proto neutron star. We have then estimated the performance of the method by
%  performing simulations with 2D core collapse supernova waveforms covering a progenitor mass range between
%  11 and 40 solar mass and different equations of state. We have shown that for Advanced LIGO and Advanced
%  Virgo detectors at design sensitivity it will be possible to infer proton neutron star properties for
%  a galactic source, while third generation detectors Einstein Telescope and Cosmic Explorer will allow
%  to test distances of several hundreds of kiloparsec.

@@

\bigskip\noindent\textit{Acknowledgments.--} Work supported by the Spanish Agencia Estatal de Investigaci\'on (PGC2018-095984-B-I00), by the Generalitat Valenciana (PROMETEO/2019/071)
and by  the European Union’s Horizon 2020 research and innovation (RISE)  programme   H2020-MSCA-RISE-2017  GrantNo.  FunFiCO-777740.  \tf{I have included my grants. Please include yours.}
N.C. acknowledges support from National Science Foundation grant PHY-1806990.

\begin{appendices}
\input{appendixA}
\end{appendices}
%\bibliographystyle{unsrt}
\bibliography{biblio}

>>>>

\begin{abstract}
The eventual detection of gravitational waves from core-collapse supernovae (CCSN) will help improve our current understanding of the explosion mechanism of massive stars. The stochastic nature of the late post-bounce gravitational wave signal due to \pcd{\sout{matter effects} the non-linear dynamics of the matter involved} and the large number of degrees of freedom of the phenomenon make the source parameter inference problem very challenging. In this paper we take a step towards that goal and present a parameter estimation approach which is based on the gravitational waves associated with \pcd{\sout{convective}} oscillations of proto-neutron stars (PNS)
\pcd{[PCD: the oscillations are driven by convection and other instabilities but I would not call them convective oscillations.]}. Numerical simulations of CCNS have shown that buoyancy-driven g-modes are responsible for a significant fraction of the gravitational wave signal and their time-frequency evolution is linked to the physical properties of the compact remnant through universal relations, as demonstrated in~\cite{Torres:2019b}. We use a set of 1D CCSN simulations to build a model that relates the  evolution of the PNS properties with the frequency of the dominant g-mode, which is extracted from the gravitational-wave data using a new algorithm we have developed for our study. The model is used to infer the time evolution of combinations \pcd{[PCD: "of a combination"? (there is only one)]} of the mass and the radius of the PNS. The performance of the method is estimated employing simulations of 2D CCSN waveforms covering a progenitor mass range between 11 and 40 solar masses and different equations of state. Considering signals embedded in Gaussian gravitational wave detector noise, we show that it is possible to infer PNS properties for a galactic source using Advanced LIGO and Advanced Virgo data at design sensitivities. Third generation detectors such as Einstein Telescope and Cosmic Explorer will allow to test distances of ${\cal O}(100\, {\rm kpc})$. %\tf{Caveats? Gaussian noise?}
% 
%  Core-collapse supernovae are very important phenomena in the Universe and their expected gravitational
%  waves emission is a promising tool to study the onset of the supernova explosion mechanism. The complexity
%  of the gravitational wave signal due to matter effects and the large degrees of freedom of the phenomena
%  makes the source parameter inference problem very challenging. In this paper, we have considered the
%  proto neutron star oscillation modes that carry out a large fraction of the gravitational wave signal and
%  whose frequency time evolution is linked to the system properties through universal relations as
%  demonstrated in ~\cite{Torres:2019b}. We have developed a simple algorithm to extract from the
%  gravitational wave data the frequency evolution of the gravity mode. A set of 1D core collapse
%  supernova simulations is used to build a model of evolution of the proto neutron star properties
%  with the gravity mode frequency. The model is then used to infer the time evolution of a combinaison of
%  the radius and mass of the proto neutron star. We have then estimated the performance of the method by
%  performing simulations with 2D core collapse supernova waveforms covering a progenitor mass range between
%  11 and 40 solar mass and different equations of state. We have shown that for Advanced LIGO and Advanced
%  Virgo detectors at design sensitivity it will be possible to infer proton neutron star properties for
%  a galactic source, while third generation detectors Einstein Telescope and Cosmic Explorer will allow
%  to test distances of several hundreds of kiloparsec.

@@

\bigskip\noindent\textit{Acknowledgments.--} Work supported by the Spanish Agencia Estatal de Investigaci\'on (PGC2018-095984-B-I00), by the Generalitat Valenciana (PROMETEO/2019/071) and by the European Union’s Horizon 2020 research and innovation (RISE) programme H2020-MSCA-RISE-2017 GrantNo. FunFiCO-777740.
N.C. acknowledges support from National Science Foundation grant PHY-1806990.
R.M. gratefully acknowledges support by the James Cook Fellowship from Government funding, administered by the Royal Society Te  Ap\={a}rangi. R.M. and P.M. also acknowledge funding from  DFG Grant KI 1443/3-2 and thank the Centre for eResearch at the University of Auckland for their technical support.
P.C.-D. acknowledges the support of the Spanish {\it Ramon y Cajal} programme (RYC-2015-19074) supporting his research.
\begin{appendices}
\input{appendixA}
\end{appendices}
%\bibliographystyle{unsrt}
\bibliography{biblio}

### 2020-11-09 conclusion.tex
My last comments.

% !TEX root = ccsn.\TeX
\section{Conclusions}
\label{sec:conclusion}

The detection of GW from CCSN may help improve our current understanding of the explosion mechanism of massive stars.  
In this paper we have provided estimates of the detectability prospects of CCSN signals using an approach based on GW associated with convective oscillations of PNS. As shown by~\cite{Torres:2019b} buoyancy-driven g-modes are excited in numerical simulations of CCSN and their time-frequency evolution is linked to the physical properties of the compact remnant through universal relations. Such modes are responsible for a significant fraction of the highly stochastic GW emitted after core bounce. The findings reported in this paper suggest that PNS asteroseismology might be within reach of current and third-generation GW detectors.

>>>>

% !TEX root = ccsn.tex
\section{Conclusions}
\label{sec:conclusion}

The detection of GW from CCSN may help improve our current understanding of the explosion mechanism of massive stars.  
In this paper we have provided estimates of the detectability prospects of CCSN signals using an approach based on GW associated with convective oscillations of PNS \pcd{[PCD: I wouldn't say "detectability prospects" since we are doing parameter estimation]}. As shown by~\cite{Torres:2019b} buoyancy-driven g-modes are excited in numerical simulations of CCSN and their time-frequency evolution is linked to the physical properties of the compact remnant through universal relations. Such modes are responsible for a significant fraction of the highly stochastic GW emitted after core bounce. The findings reported in this paper suggest that PNS asteroseismology might be within reach of current and third-generation GW detectors.

### 2020-11-09 introduction.tex
My last comments.

The life of sufficiently massive stars, i.e.~those born with masses between $\sim 8$~M$_\odot$ and $\sim 120$~M$_\odot$, ends with the collapse of {the} iron core under {its} own gravity, leading {to} the formation of a neutron star {(NS)} or a black hole (BH), {and} followed (typically but not necessarily in the BH case) by {a supernova} explosion. Nearby core-collapse supernova (CCSN) explosions are expected to be sources of gravitational waves (GWs) and they could be 
%are one of the main candidates for 
the next great discovery of current ground-based observatories. However, these are relative rare events. A neutrino-driven explosion \citep{Bethe:1990} is the most likely outcome in the case of slowly rotating cores, which are present in the bulk of CCSN progenitors. The emitted GWs could be detected with the advanced ground-based GW detector network, Advanced LIGO (aLIGO)~\citep{TheLIGOScientific:2014jea}, Advanced Virgo (AdV)~\citep{TheVirgo:2014hva} and
KAGRA~\citep{Aso:2013eba}, within $\sim 5$~kpc \citep{Gossan:2016,TargetedSNSearchO12}. Such a galactic event has a rate of about $2-3$ per century \citep{Adams:2013,Rozwadowska:2021}.
For the case of rapidly rotating progenitor cores the result is likely a magneto-rotational explosion, yielding  a more powerful GW signal that could be detected within $50$~kpc and, for some extreme models, up to $5-30$ Mpc \citep{Gossan:2016,TargetedSNSearchO12}. However, only about $1\%$ of the electromagnetically observed events show signatures of fast rotation (broad-lined type Ic SNe \citep{Li:2011b} or events associated with long GRBs 
\citep{Chapman:2007}) making this possibility a subdominant channel of detection with an event rate of $\sim 10^{-4} \rm{yr}^{-1}$\mab{[add ref?]}. For the results discussed in this work we only consider neutrino-driven CCSN.
%\tf{This last sentence must be mentioned somewhere (or maybe not) but perhaps here is not the best place.}\mab{MAB:I'm in favor of deleting it as it is rather obvious we are considering neutrino driven CCSN} Despite the low rates, CCSN are of great scientific interest because they produce complex GW signals which could provide significant clues about the physical processes at work after the gravitational collapse of stellar cores.

@@

Using results from 2D CCSN numerical simulations as a background with respect to which to solve an eigenvalue problem~\citep{Torres:2018, Torres:2019a} found that the eigenmode spectrum of the region within the shock (including the PNS and the post-shock region) 
shows a good match to the mode frequencies and to the features observed in the GW spectrum of the same simulations (specially when space-time perturbations are included \citep{Torres:2019a}). \tf{This last sentence might be improved.} \mab{MAB: What about: Computing the mode spectrum of the region within the shock (including the PNS and the post-shock region) consists in solving an eigenvalue problem using background simulations. Using results from 2D CCSN numerical simulations \citep{Torres:2018, Torres:2019a} found that the eigenmode spectrum shows a good match to the mode frequencies and to the features observed in the GW spectrum of the same simulations (specially when space-time perturbations are included \citep{Torres:2019a}). }

>>>>

The life of sufficiently massive stars, i.e.~those born with masses between $\sim 8$~M$_\odot$ and $\sim 120$~M$_\odot$, ends with the collapse of {the} iron core under {its} own gravity, leading {to} the formation of a neutron star {(NS)} or a black hole (BH), {and} followed (typically but not necessarily in the BH case) by {a supernova} explosion. Nearby core-collapse supernova (CCSN) explosions are expected to be sources of gravitational waves (GWs) and they could be 
%are one of the main candidates for 
the next great discovery of current ground-based observatories. However, these are relative rare events. A neutrino-driven explosion \citep{Bethe:1990} is the most likely outcome in the case of slowly rotating cores, which are present in the bulk of CCSN progenitors. The emitted GWs could be detected with the advanced ground-based GW detector network, Advanced LIGO (aLIGO)~\citep{TheLIGOScientific:2014jea}, Advanced Virgo (AdV)~\citep{TheVirgo:2014hva} and
KAGRA~\citep{Aso:2013eba}, within $\sim 5$~kpc \citep{Gossan:2016,TargetedSNSearchO12}. Such a galactic event has a rate of about $2-3$ per century \citep{Adams:2013,Rozwadowska:2021}.
For the case of rapidly rotating progenitor cores the result is likely a magneto-rotational explosion, yielding  a more powerful GW signal that could be detected within $50$~kpc and, for some extreme models, up to $5-30$ Mpc \citep{Gossan:2016,TargetedSNSearchO12}. However, only about $1\%$ of the electromagnetically observed events show signatures of fast rotation (broad-lined type Ic SNe \citep{Li:2011b} or events associated with long GRBs 
\citep{Chapman:2007}) making this possibility a subdominant channel of detection with \pcd{a galactic} event rate of $\sim 10^{-4} \rm{yr}^{-1}$\mab{[add ref?]}\pcd{[PCD: This number is just ~1\% of the galactic rate of 2-3 per century, so no reference is needed]}. For the results discussed in this work we only consider neutrino-driven CCSN \pcd{of non-rotating stellar cores} .
%\tf{This last sentence must be mentioned somewhere (or maybe not) but perhaps here is not the best place.}\mab{MAB:I'm in favor of deleting it as it is rather obvious we are considering neutrino driven CCSN} Despite the low rates, CCSN are of great scientific interest because they produce complex GW signals which could provide significant clues about the physical processes at work after the gravitational collapse of stellar cores.

@@

Using results from 2D CCSN numerical simulations as a background \pcd{\sout{with respect to which to solve an eigenvalue problem}}~\citep{Torres:2018, Torres:2019a} found that the eigenmode spectrum of the region within the shock (including the PNS and the post-shock region) 
shows a good match to the mode frequencies and to the features observed in the GW spectrum of the same simulations (specially when space-time perturbations are included \citep{Torres:2019a}). \tf{This last sentence might be improved.} \mab{MAB: What about: Computing the mode spectrum of the region within the shock (including the PNS and the post-shock region) consists in solving an eigenvalue problem using background simulations. Using results from 2D CCSN numerical simulations \citep{Torres:2018, Torres:2019a} found that the eigenmode spectrum shows a good match to the mode frequencies and to the features observed in the GW spectrum of the same simulations (specially when space-time perturbations are included \citep{Torres:2019a}). } \pcd{[PCD: I am not convinced about the first sentence of mab's proposal. Maybe if we just delete "with respect to which to solve an eigenvalue problem"
the sentence becomes more readable]}

### 2020-11-09 methods.tex
update plots & text
My last comments.

\begin{figure}[t]
 \centering
 \includegraphics[width=0.45\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from our 25 1D simulations of the model set. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points. \tf{18 or 25?} \tf{We could remove the legend as only one code is used.} } 
 \label{fig:LMVAR}
\end{figure}

We next outline our strategy for estimating the time evolution of $r(t)$
%ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ (in units of solar mass and km) 
from the observation of the $\mbox{}^2g_2$ oscillation mode in the GW detector data.
%An integral part of this strategy is the universal relations that relate the
%characteristic frequency of the PNS oscillation $f$, $g$ and $p$ modes with the mass
%and the radius of the PNS, the shock radius and the total mass inside the shock as
%demonstrated in \cite{Torres:2019b}.
To build the model of the ratio $r$ as a function of the frequency $f$ we use the 
1D simulations of the {\it model set}. Figure~\ref{fig:LMVAR}
shows the data for the $25$ numerical simulations. 
%As identified by \cite{Torres:2019b}, the only systematic deviation from a single universal relation is the numerical code used in the simulations. 
%To avoid any systematic effect, we only use the $18$ simulations performed with the {\sc AENUS-ALCAR}
%code, which is the same code that was used in our test set.
%\mab{We defer a discussion of the possible consequences of this choice in Section \ref{sec:conclusion}.}
%The consequences of this choice are discussed in the conclusions.
Using these data we parametrize the discretized ratio $r_i$ with a cubic polynomial
regression with heteroscedastic errors
\begin{equation}
\label{eq:model1}
r_i=\beta_1 f_i + \beta_2 f_i^2 +\beta_3 f_i^3 + \epsilon_i\,,
\end{equation}
where $\epsilon_i$ are assumed to be independent zero-mean Gaussian errors with
variances $\sigma_i^2$ that increase with frequency $f_i$. The model for frequency-dependent
variances is
\begin{equation}
\log \sigma_i=\alpha_0+ \alpha_1 f_i + \alpha_2 f_i^2 + \delta_i\,,
\end{equation}
with independent and identically zero-mean Gaussian errors $\delta_i$. The R-package \texttt{lmvar}
\cite{lmvar:2019} that implements a maximum likelihood approach was used to fit the model.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolate $f(t)$
for values in between $t_i$. We then use our model given by Eq.~\eqref{eq:model1} to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An example is given in Figure \ref{fig:ratio} where the red triangles are the point estimates and
the grey bands represent 95\% confidence bands. The size of the red triangles is proportional to the magnitude of the $\mbox{}^2 g_2$-mode estimates.  Note that as the frequency of the $\mbox{}^2 g_2$-mode becomes higher our estimates show more uncertainty (bigger intervals) because our model allows for heterogeneous variance. Ratio values
computed using the mass and radius values obtained from the simulation code (i.e.~the true values)
are shown in black. In this example of a noise-free GW signal the coverage of our 95\% confidence band is 100\%
of the true values. In the next section we investigate the performance of the reconstruction of $r(t)$ when the GW
signal is embedded in noise. We also note that despite we have only explicitely shown results for the GW signal of the {\texttt s20S} model the same conclusions hold for any of the other waveforms of our test set.

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/ratio}
 \caption{Comparison of the time evolution of the ratio $M_{\rm PNS}/R_{\rm PNS}^2$ estimated from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (shown by open triangles and by the 95\% confidence belt in grey) against the value derived from the PNS mass and radius given by the simulation code (shown by filled black circles).  The ratios are represented proportionally to the magnitude of the $\mbox{}^2 g_2$-mode estimates.}
 \label{fig:ratio}
\end{figure}

>>>>

\begin{figure}[t]
 \centering
 \includegraphics[width=0.45\textwidth]{plots/model}
 \caption{Ratio $M_{\rm PNS}/R_{\rm PNS}^2$ from our \pcd{18} 1D simulations of the model set. The solid line is the maximum likelihood estimate of heteroscedastic cubic model with 95\% confidence bands (dashed lines) considering the 18 simulation data points.  } 
 \label{fig:LMVAR}
\end{figure}

We next outline our strategy for estimating the time evolution of $r(t)$
%ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ (in units of solar mass and km) 
from the observation of the $\mbox{}^2g_2$ oscillation mode in the GW detector data.
%An integral part of this strategy is the universal relations that relate the
%characteristic frequency of the PNS oscillation $f$, $g$ and $p$ modes with the mass
%and the radius of the PNS, the shock radius and the total mass inside the shock as
%demonstrated in \cite{Torres:2019b}.
To build the model of the ratio $r$ as a function of the frequency $f$ we use the 
1D simulations of the {\it model set}. Figure~\ref{fig:LMVAR}
shows the data for the $25$ numerical simulations. 
%As identified by \cite{Torres:2019b}, the only systematic deviation from a single universal relation is the numerical code used in the simulations. 
%To avoid any systematic effect, we only use the $18$ simulations performed with the {\sc AENUS-ALCAR}
%code, which is the same code that was used in our test set.
%\mab{We defer a discussion of the possible consequences of this choice in Section \ref{sec:conclusion}.}
%The consequences of this choice are discussed in the conclusions.
Using these data we parametrize the discretized ratio $r_i$ with a cubic polynomial
regression with heteroscedastic errors
\begin{equation}
\label{eq:model1}
r_i=\beta_1 f_i + \beta_2 f_i^2 +\beta_3 f_i^3 + \epsilon_i\,,
\end{equation}
where $\epsilon_i$ are assumed to be independent zero-mean Gaussian errors with
variances $\sigma_i^2$ that increase with frequency $f_i$. The model for frequency-dependent
variances is
\begin{equation}
\log \sigma_i=\alpha_0+ \alpha_1 f_i + \alpha_2 f_i^2 + \delta_i\,,
\end{equation}
with independent and identically zero-mean Gaussian errors $\delta_i$. The R-package \texttt{lmvar}
\cite{lmvar:2019} \pcd{[PCD: reference is empty]} that implements a maximum likelihood approach was used to fit the model.

@@

We collect the instantaneous frequency $f(t_i)$ corresponding to the ridge $m(t_i)$ for
the midpoint $t_i$ of each local time interval of the spectrogram and interpolate $f(t)$
for values in between $t_i$. We then use our model given by Eq.~\eqref{eq:model1} to obtain
estimates of the time evolution of the ratio together with 95\% confidence intervals.
An example is given in Figure \ref{fig:ratio} where the red triangles are the point estimates and
the grey bands represent 95\% confidence bands. The size of the red triangles is proportional to the magnitude of the $\mbox{}^2 g_2$-mode \pcd{frequency?} estimates.  
\pcd{[PCD: By magnitude you mean the value of the frequency? ]}
Note that as the frequency of the $\mbox{}^2 g_2$-mode becomes higher our estimates show more uncertainty (bigger intervals) because our model allows for heterogeneous variance. Ratio values
computed using the mass and radius values obtained from the simulation code (i.e.~the true values)
are shown in black. In this example of a noise-free GW signal the coverage of our 95\% confidence band is 100\%
of the true values. In the next section we investigate the performance of the reconstruction of $r(t)$ when the GW
signal is embedded in noise. We also note that despite we have only explicitely shown results for the GW signal of the {\texttt s20S} model the same conclusions hold for any of the other waveforms of our test set.

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{plots/ratio}
 \caption{Comparison of the time evolution of the ratio $M_{\rm PNS}/R_{\rm PNS}^2$ estimated from the $\mbox{}^2 g_2$-mode of the {\texttt s20S} signal (shown by open triangles and by the 95\% confidence belt in grey) against the value derived from the PNS mass and radius given by the simulation code (shown by filled black circles).  The ratios \pcd{[PCD: size of the triangles?]} are represented proportionally to the magnitude of the $\mbox{}^2 g_2$-mode \pcd{frequency?} estimates.}
 \label{fig:ratio}
\end{figure}

### 2020-11-09 results.tex
My last comments.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_coverage_allwvfs}
 \caption{Median of the coverage for the eight CCSN waveforms of the {\it test set} embedded in aLIGO noise as a function of the  distance to the source. \mab{The ``no signal'' line shows the median of coverage in absence of any signal. In this example, the median is null and overlaps with the horizontal axis. The blue band boundaries are given by the $\mathrm{5^{th}}$ and $\mathrm{95^{th}}$ percentiles of coverage in absence of any signal.}} \label{fig:aLIGO_cov_allwvf}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{plots/s20--SFHo_all3G}
  \caption{Median of the relative error $\Delta$ as a function of the  distance to the source for the CCSN waveform model {\texttt s20S} embedded in third-generation detector noise.}
  \label{fig:s20--SFHo_all3G}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_coverage_allwvfs}
 \caption{Median of the coverage for the eight CCSN waveforms of the {\it test set} embedded in aLIGO noise as a function of the  distance to the source\pcd{[PCD: if the solid line is the median, what are the symbols? Same for figures 6 and 7.]}. \mab{The ``no signal'' line shows the median of coverage in absence of any signal. In this example, the median is null and overlaps with the horizontal axis. The blue band boundaries are given by the $\mathrm{5^{th}}$ and $\mathrm{95^{th}}$ percentiles of coverage in absence of any signal.}} \label{fig:aLIGO_cov_allwvf}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{plots/s20--SFHo_all3G}
  \caption{Median of the relative error $\Delta$ as a function of the  distance to the source for the CCSN waveform model {\texttt s20S} embedded in third-generation detector noise. \pcd{[PCD: Should we show the corresponding
  blue ranges for the pure noise case?]}}
  \label{fig:s20--SFHo_all3G}
\end{figure}

### 2020-11-09 simulations.tex
My last comments.

For the {\it model set}, we use the $25$ spherically symmetric (1D) simulations of \citep{Torres:2019a}
including progenitors with zero-age main sequence (ZAMS) masses in the range 
$M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$. The set contains simulations using  
six different EOS. Details can be found in
 \citep{Torres:2019a}. The reason to use 1D simulations for the model set
 is that their computational cost is significantly smaller than that of multidimensional
 simulations which allows us to accumulate the statistics necessary to build a good model for $r(f)$.
 {For each time of each simulation we compute the ratio $r$ and the frequency of the $^2g_2$ mode by means of the linear analysis
 described in \cite{Torres:2018,Torres:2019a,Torres:2019b}. }

>>>>

For the {\it model set}, we use the \pcd{$18$ }spherically symmetric (1D) simulations of \citep{Torres:2019a}
including progenitors with zero-age main sequence (ZAMS) masses in the range 
$M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$. The set contains simulations using  
six different EOS. Details can be found in
 \citep{Torres:2019a}. The reason to use 1D simulations for the model set
 is that their computational cost is significantly smaller than that of multidimensional
 simulations which allows us to accumulate the statistics necessary to build a good model for $r(f)$.
 {For each time of each simulation we compute the ratio $r$ and the frequency of the $^2g_2$ mode by means of the linear analysis
 described in \cite{Torres:2018,Torres:2019a,Torres:2019b}. }
